Evaluating the Performance and Energy Efficiency of the COSMO-ART model system

### 2014-04-25 trunk/paper_enahpc14/Sec4:Experimental-results.tex
modifies ETS and TTS figures for MPI blocking and polling modes

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-1.eps}
  \caption{Time-to-solution and energy-to-solution on
    \textsc{Tintorrum} - Polling mode}
  \label{fig:4}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-2.eps}
  \caption{Time-to-solution and energy-to-solution on
    \textsc{Tintorrum} - Polling mode}
  \label{fig:5}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-3.eps}
  \caption{Time-to-solution and Power on \textsc{Tintorrum} - Polling
    mode}
  \label{fig:6}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-4.eps}
  \caption{Time-to-solution and Power on \textsc{Tintorrum} - Blocking
    mode}
  \label{fig:7}
\end{figure}

>>>>

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-5.eps}
  \caption{Mean time-to-solution and energy-to-solution on
    \textsc{Tintorrum} - MPI Polling and Blocking modes}
  \label{fig:4}
\end{figure}
